Real-world Feasibility Analysis of ACT Algorithm for Robotic Manipulation on Home

### 2025-05-03 paper.tex
feat: 添加 ACT 稳健性相关的描述

Action chunking mitigates error accumulation in long-horizon tasks~\cite{ref10}, the integrated task execution achieved a 60\% success rate (6/10) when sequentially deploying all models to complete the full Tower of Hanoi task.

>>>>

Action chunking helps mitigate error accumulation in long-horizon tasks~\cite{ref10}. In our evaluation, sequentially deploying all models to complete the full Tower of Hanoi task achieved a 60\% success rate (6/10). Most failures were due to grasping the wrong disk or misalignment during placement, causing the disk to fall. Given that the Tower of Hanoi task requires high precision in execution, our current priority is to ensure accurate completion of the task sequence. In more open environments—such as those with human presence, lighting variation, or camera shifts—such errors may be amplified, and system robustness remains a key challenge.To address this, we propose two future directions: (1) applying reinforcement learning fine-tuning to error-prone action segments to enable adaptive correction, and (2) integrating visual-feedback-based online correction, such as retrying failed grasps. While these approaches are not implemented in this work, they hold promise for future research.

Moreover, task generalization—such as handling varied initial configurations of the Tower of Hanoi—will be an important direction for future evaluation. This would place higher demands on the model’s adaptability and policy stability. Achieving such generalization is expected to require larger-scale datasets and significantly longer training durations. Given the already considerable challenge of ensuring accurate task execution, our current efforts focus on precision, laying the groundwork for subsequent generalization studies.
